\section{Concluding remarks and recommendations}
\label{sec:conclusions}

This trade-study laid out technical requirements, science goals, opportunities, and risks relevant to observing with \tess after its first two years.
The baseline science requirements for \tesss Primary Mission are 
defined~\citep{ricker_transiting_2014}, and an Extended Mission offers the
whole community a chance to re-prioritize.
Is securing \tesss ephemerides more important than trying to detect more
planets at longer orbital periods? 
Are the variations in absolute new planet yields, at $\lesssim30\%$ between all 
the Extended Missions, more valuable than other desires and opportunities?
We leave these questions open for the community to discuss at the \tess 
Wiki\textsuperscript{\ref{fn:wiki}}.


\subsection{Recommendations}
\label{sec:recommendations}
\begin{description}
  
	\item[Analyze target prioritization problem] and decide whether or not to optimize target selection based on results. %for instance \'a la~\protect\citet{kipping_transit_2016}. 
	Planet occurrence rates are functionally dependent on a star's properties -- should this affect which stars we give upgraded cadence?
	Is our proposed \texttt{Merit} statistic (Eq.~\ref{eq:merit}) how we want to prioritize targets?
	
      \item[Optimize cadence:] observing $4\times10^5$ target stars at 
	      4 minute cadence, rather than $2\times10^5$ at 2 minute cadence,
	      would allow the FFIs to be returned at a higher cadence.
	      This could in turn improve prospects for transit detection.  
	      (Preliminary numerical experiments indicate that this is indeed the 
	      case).
	      
	      In addition, a metric should be devised that
        quantifies, for each star, how much {\it improvement} would
        result from observing at short-cadence versus long-cadence.
        We could then prioritize the stars for which short-cadence 
        delivers the most significant benefit. 
        For instance if the number of short-cadence stars could be 
        greatly reduced with little effect on the planet detection
        statistics, then this would allow the FFIs to be returned at a
        higher cadence, which could be desirable.
	
	\item[Take steps to address the `upgrading cadence' problem:]
          if there is a likely transiting planet in full frame image
          data, upgrading the planet to short cadence in future
          observing sectors improves the probability and fidelity of
          detection. How is this being addressed for the Primary Mission?
          Could this be an argument to observe the southern
          sky in year 3, in order to have extra time to prepare?
	
	\item[Guest Investigator Office or \tess Science Office should
          solicit advice] from experts in asteroseismology and
          variable-sky astronomy to understand how Extended Missions
          affect their science cases (\textit{e.g.}, data throughput
          rates are particularly important for time-sensitive
          supernovae observations).  More broadly, solicit community
          feedback during the process of defining the Extended
          mission.  This may entail a call for white papers, comments
          on this report, or direct proposals to the GI office.  As
          exemplified in NASA’s 2016 Astrophysics Senior Review,
          everyone benefits from the discussions generated by such
          community feedback~\citep{donahue_senior_2016}.
	
	\item[Decide (explicitly or implicitly) on weights between our
          proposed metrics.]  Perhaps also brainstorm others --
          Sec.~\ref{sec:comparing_pointing_strategies} gives a
          summarized list.  Are the $\lesssim30\%$ variations in
          absolute new planet yields more valuable than other desires
          or opportunities?
	
	\item[Simulate combining \tess and \ktwo data from
          \rm{\elong\:} \textit{and} \rm{\eshort}.]  This is perhaps
          the most important qualitative difference between observing
          towards and away from the ecliptic.  Would \tess\!+\ktwo
          enable more discoveries out at long periods than
          alternatives?  How many of the new planets that \tess
          detects on the ecliptic will actually be detected by \ktwo?
          Is the value-added of combining datasets a compelling case
          compared with discovery?
          
    \item[Ensure {\rm \npole} adequately mitigates scattered sunlight.]
    See description in Sec.~\ref{sec:proposed_pointings}.
	
	\item[Further topics for study:]
	\ 
	
	\textit{1.)}
	How can a particular Extended Mission scenario reduce risk for measuring 
	masses of 50 rocky planets (a baseline \tess science requirement)?
	
	\textit{2.)}
	After how many years would the planet yield start to show steeply diminishing returns?
	Suppose, for example, the Primary Mission were repeated indefinitely.
  How much dimmer would the host stars of new planets be, in each year?
	Would the planets tend to be smaller?
	Would there be fewer of them?
	
	\textit{3.)}
	Study the limiting case of \hemis\:for 2 years, vs Primary Mission repeat 
	for 2 years. The most interesting aspect of this comparison is the 
	continuous viewing zones: 2 CVZs with 14-day window functions over 2 years, 
	vs. 2 CVZs with continuous sampling for one-year each.\footnote{Our 
	simplified perfect period extraction would miss deleterious effects from the 
	uneven sampling.}
\end{description}
