\section{Statement of problem}
\label{sec:statement_of_problem}
Once \tesss primary survey is complete, what should the spacecraft do next? 
Different observing strategies may benefit different science goals. 
As a preliminary example, observing a given region of sky for as long as possible allows \tess to detect planets with the longest possible orbital periods.
However, if we want to discover new small planets around the brightest possible stars, it may behoove us to target new sky, perhaps near the ecliptic.

% Could add a paragraph here about relevant timeline. Launch 20 Dec 2017, commisioning for 2 months, begin sky survey early March 2018. Senior review is ~Feb/March 2020.
% We might have extra funding for a third year -- we'll see. We'll need to know what we're going to do by early 2020 though.

This memo is a trade study of a non-exhaustive set of plausible extended mission scenarios. 
Our main aim is to quantify how different spacecraft-pointings will affect \tesss planet yield.
We also discuss different opportunities that may become available by observing different regions of sky.

%Beyond just where the spacecraft points, different data collection strategies also influence detection outcomes.
Some important free parameters that will define \tesss extended mission include:
\begin{itemize}
	\item Where to point the cameras on the sky.
	\item The duration of proposed observations.
	\item With a fixed data mass, the relative allocations between short (2 minute) and long (30 minute) cadence images\footnote{Respectively referred to as `postage stamps' because the aperture centered on any given star resembles a small-area postage-stamp, and as `full frame images' since they are the entire CCD readout. The `postage stamp' target stars are a subset, nominally $2\times 10^5$ stars, of the \tess Input Catalog.}. 
	\item The cadence of full frame images; for instance keeping full-frames at 15 minute cadence at the cost of observing fewer short-cadence targets.
	\item The cadence of postage stamps; for instance stacking them at 4 minute cadence instead of 2 minute cadence, and observing twice as many target stars.
	\item The target allocation strategy. This includes how to prioritize target stars from the \tess Input Catalog. It also involves the question of how to use knowledge obtained from full frame images in the primary mission when re-observing the same fields in an extended mission.
\end{itemize}

In this report, we evaluate how well a set of extended mission spacecraft pointings (for 1 year of extra observing) satisfies different technical requirements and science goals. 
We also discuss unique opportunities that may be available through each option.
The other parameters outlined above, notably the relative allocations between different data products at a fixed data mass, will also impact the primary and extended missions. We recommend that they be studied separately.


\subsection{Outline of report}
We begin in Sec.~\ref{sec:approach} by discussing how we select and compare different pointing strategies, as well as how we model \tesss observations and planet detections.
We then compare the newly detected planet populations from some plausible one-year extended missions in Sec.~\ref{sec:newly_detected_planet_metrics}. 
Critically, newly detected planets are not the only valuable outcome of an extended mission. 
In Sec.~\ref{sec:broader_science_beyond_planet_detection_stats}, we thus highlight some of the broader science that \tess could and perhaps should perform beyond new planet detections.
%for instance asteroseismology, open cluster observations, supernovae detections, eclipsing binary studies, main-belt asteroid observations, and others. 
We go on to discuss opportunities, notably for ground and space-based follow-up, as well as risks that could come from each observing strategy in Sec.~\ref{sec:risks_opps}.
%This entails considering the implications of each scenario for ground and space-based follow-up, and also noting the effect extended missions could have on the .
%Our results in Secs.~\ref{sec:newly_detected_planet_metrics} and~\ref{sec:broader_science_beyond_planet_detection_stats} generalize to two-year scenarios.
%We proceed by discussing 
%While we frame our study in a way that we can make precise statements, the accuracy of our predictions is contingent upon \tesss in-flight performance. 
We conclude in Sec.~\ref{sec:conclusions} with recommendations for what comes next in defining \tesss extended mission.
%The appendix (Sec.~\ref{sec:appendix}) covers methods behind our planet detection simulation, and summarizes the most important results and metrics in a color-coded spreadsheet.
